Russian sanctions figures

### 2024-03-13 ms-russia-figures.Rmd
Add exploratory figures to identify source of consumption spike

@@

@@

>>>>

To do: 
-

@@

# Product metadata dataframe
product <- dbGetQuery(con, "SELECT * FROM products") %>%
  select(-record_id)

@@

```{r}
# Explore spike in China's apparent consumption of Russian products
tmp <- consumption %>% 
  filter(source_country_iso3c == "RUS", consumer_iso3c != "RUS") %>%
  group_by(year, consumer_iso3c) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

consumption %>% 
  filter(source_country_iso3c == "RUS", consumer_iso3c == "CHN") %>%
  group_by(year) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ggplot(aes(x = year, y = consumption_live_t)) +
  geom_line() + 
  theme_bw()

tmp <- consumption %>% 
  filter(source_country_iso3c == "RUS", consumer_iso3c == "CHN") %>%
  group_by(year, sciname_hs_modified) %>% 
  summarise(consumption_live_t = sum(consumption_live_t, na.rm = TRUE))

prod %>% 
  filter(iso3c == "RUS", sciname == "gadus chalcogrammus") %>%
  group_by(year) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  ggplot(aes(x = year, y = live_weight_t)) +
  geom_line() +
  theme_bw()

artis %>% 
  filter(exporter_iso3c == "RUS", importer_iso3c == "CHN") %>%
  plot_ts(artis_var = "hs6", plot.type = "filled", prop_flow_cutoff = 0.07)

artis %>% 
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN") %>%
  group_by(year) %>%
  summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
  ggplot(aes(year, live_weight_t)) +
  geom_line() +
  theme_bw()

artis %>% 
  filter(source_country_iso3c == "RUS", exporter_iso3c == "CHN") %>%
  plot_ts(artis_var = "importer_iso3c", plot.type = "filled")

artis %>% 
  filter(hs6 %in% c(30379, 30380, 303429, 30499, 30510, 30520, 
                    30530, 30549, 30569, 51191, 1400410, 140420,
                    160419, 160430), exporter_iso3c == "CHN") %>%
  plot_ts(artis_var = "hs6", plot.type = "filled")
